All chemical mechanisms were adapted into the modularised KPP \citep{Damian:2002} format from their original format for use in the MECCA boxmodel \citep{Sander:2011}.
test

The MCM v3.2 \citep{Jenkin:1997, Jenkin:2003, Saunders:2003, Bloss:2005, MCM_Site} was the reference mechanism. 
Its approach to inorganic chemistry, dry deposition, photolysis and treatment of peroxy radical--peroxy radical reactions were applied to all mechanisms. 

\subsection{Photolysis} \label{ss:photolysis}
Photolysis was parameterised as a function of the solar zenith angle as per the MCM approach \citep{Saunders:2003}. 
Mechanism species with a direct MCM v3.2 counterpart were assigned the corresponding MCM v3.2 photolysis rate parameter. 
Otherwise the mechanism's literature was used to determine the appropriate MCM v3.2 photolysis rate parameter. 
In some cases this was the MCM v3.2 photolysis rate parameter closest in magnitude to that specified in the mechanism. 

For example, in RACM2 the organic nitrate species ONIT has a photolysis rate of $1.96 \times 10^{-6}$ s$^{-1}$ that was compared to the MCM v3.2 organic nitrate photolysis rate parameters (J$_{51}$ -- J$_{57}$). 
The rate parameter J$_{54}$ was the most similar and this was assigned as the ONIT photolysis rate parameter in RACM2.

Photolysis of a mechanism species was sometimes represented by more than one \mbox{MCM v3.2} photolysis reaction. 
The product yield of the original mechanism reaction was preserved by using a combination of the MCM v3.2 rate parameters. 
For example, the photolysis of methyl vinyl ketone (MVK) in MOZART-4 is described by the reaction
\begin{reactionlist}
    \reactionitem{\ce{MVK + h$\nu$}}{0.7 CO + 0.7 \ce{C3H6} + 0.3 \ce{CH3O2} + 0.3 \ce{CH3CO3}}{new}{r:MVK_hv_MOZ}
\end{reactionlist} 
Whereas in the MCM v3.2 it is described by two reactions
\begin{reactionlist}
    \reactionitem{\ce{MVK + h$\nu$}}{\ce{C3H6 + CO}}{new}{r:MVK_hv_MCM_1}
    \reactionitem{\ce{MVK + h$\nu$}}{\ce{CH3CO3 + CO + HCHO + HO2}}{new}{r:MVK_hv_MCM_2}
\end{reactionlist}
where the photolysis parameters for reactions \reactionref{r:MVK_hv_MCM_1} and \reactionref{r:MVK_hv_MCM_2} are designated as J$_{23}$ and J$_{24}$,
respectively. 
In order to keep the product yield as prescribed in MOZART-4, the photolysis rate parameter assigned to MVK photolysis using the MOZART-4 mechanism is \mbox{$0.7$ J$_{23}$ + $0.3$ J$_{24}$}.


\subsection{Organic Peroxy Radical Self and Cross Reactions} \label{ss:peroxy_radical_reactions}
{
    \renewcommand{\arraystretch}{1.3}
    \begin{table}
        \begin{center}\small
            \begin{tabular}{lP{8.8cm}P{2.8cm}}
                \hline \hline
                \textbf{Mechanism} & \textbf{Reaction} & \textbf{Rate Constant} \\ \hline \hline
                \multirow{3}{*}{MCM v3.2} & C2H5O2 = C2H5O & \textit{k}*RO2*$0.6$ s$^{-1}$ \\
                & C2H5O2 = C2H5OH & \textit{k}*RO2*$0.2$ s$^{-1}$ \\
                & C2H5O2 = CH3CHO & \textit{k}*RO2*$0.2$ s$^{-1}$ \\ \hline 
                \multirow{3}{*}{MOZART-4} & C2H5O2 + CH3O2 = $0.7$ CH2O + $0.8$ CH3CHO + HO2 \newline \hspace*{3.5cm} + $0.3$ CH3OH + $0.2$ C2H5OH & $2 \times 10^{-13}$ cm$^3$ molecules$^{-1}$ s$^{-1}$ \\
                & C2H5O2 + C2H5O2 = $1.6$ CH3CHO + $1.2$ HO2 \newline \hspace*{3.5cm} + $0.4$ C2H5OH & $6.8 \times 10^{-14}$ cm$^3$ molecules$^{-1}$ s$^{-1}$\\ \hline 
                MOZART-4 & \multirow{2}{*}{C2H5O2 = $0.8$ CH3CHO + $0.6$ HO2 + $0.2$ C2H5OH} & \multirow{2}{*}{$2 \times 10^{-13}$*RO2 s$^{-1}$} \\
                modified & & \\ \hline \hline
            \end{tabular}
            \caption{Ethyl peroxy radical (\ce{C2H5O2}) self and cross organic peroxy reactions in the MCM v3.2 and MOZART-4 mechanisms including rate constants. \mbox{\textit{k} = $2$($6.6 \times 10^{-27}\exp(365/T))^{\frac{1}{2}}$ molecules$^{-1}$ s$^{-1}$} and RO2 is the sum of all organic peroxy radical mixing ratios.}
            \label{t:RO2}
        \end{center}
    \end{table}
}

{
    \renewcommand{\arraystretch}{1.3}
   \begin{table}
        \begin{center}\small
            \begin{tabular}{lP{6.8cm}P{4.8cm}}
                \hline \hline
                \textbf{Reactants} & \textbf{Products} & \textbf{Rate Constant} \\ \hline \hline
                \multirow{2}{*}{MO2 + MO2} & \multirow{2}{*}{$0.74$ HO2 + $1.37$ HCHO + $0.63$ MOH} & $9.4 \times 10^{-14}\exp{(390/T)}$ \\ & & cm$^3$ molecules$^{-1}$ s$^{-1}$ \\
                \multirow{2}{*}{MO2} & \multirow{2}{*}{$0.37$ HO2 + $0.685$ HCHO + $0.315$ MOH} & $9.4 \times 10^{-14}\exp{(390/T)}$*RO2 \\ & & s$^{-1}$ \\ \hline
                \multirow{2}{*}{ETHP + MO2} & HO2 + $0.75$ HCHO + $0.75$ ACD & $1.18 \times 10^{-13}\exp{(158/T)}$ \\ & \hspace*{5mm} + $0.25$ MOH + $0.25$ EOH & cm$^3$ molecules$^{-1}$ s$^{-1}$ \\
                \multirow{2}{*}{ETHP} & $0.63$ HO2 + $0.065$ HCHO + $0.75$ ACD  & $1.18 \times 10^{-13}\exp{(158/T)}$*RO2 \\ & \hspace*{5mm} + $0.25$ EOH & s$^{-1}$ \\ \hline \hline
            \end{tabular}
            \caption{Dermination of ETHP pseudo-unimolecular reaction and rate constant in RACM2 including rate constants. RO2 is the sum of all organic peroxy radical mixing ratios.}
            \label{t:ETHP}
        \end{center}
    \end{table}
}

Reactions of organic peroxy radicals (\ce{RO2}) with other organic peroxy radicals are divided into self (\ce{RO2 + RO2}) and cross (\ce{RO2} + R$^{\prime}$\ce{O2}) reactions. 
These reactions are typically represented in chemical mechanisms as bimolecular reactions which would cause ambiguities when implementing the tagging scheme. 
Namely, which tag to be used for the products of reactions between \ce{RO2} having different tags. 
To avoid such ambiguities, the MCM v3.2 approach to self and cross \ce{RO2} reactions is used -- all \ce{RO2} react with \ce{RO2} and R$^{\prime}$\ce{O2} at a single uniform rate. 
This was represented as a pseudo-unimolecular reaction whose rate constant includes a factor `RO2' which was the sum of the mixing ratios of all organic peroxy radicals \citep{Saunders:2003}.

The pseudo-unimolecular reaction products and their yields were determined either by using the \ce{RO2 + RO2} reaction and halving the product yields. 
This is demonstrated for the MOZART-4 treatment of the ethyl peroxy radical in Table \ref{t:RO2}. 
Alternatively, the \ce{RO2 + CH3O2} reaction was used and the products due to \ce{CH3O2} were removed. 
Table \ref{t:ETHP} outlines the steps taken to determine the ETHP pseudo-unimolecular reaction in RACM2. 

First the products due to MO2, which represents \ce{CH3O2} in RACM2, are determined as outlined above using the \mbox{MO2 + MO2} reaction. 
The MO2 product yields are then subtracted from the \mbox{ETHP + MO2} reaction. 
Any products having a negative yield were not included in the final pseudo-unimolecular reaction.

The methyl acyl peroxy radical (\ce{CH3C(O)O2}) was the exception to the above approach. 
Although most mechanisms include a \mbox{\ce{CH3C(O)O2 + CH3C(O)O2}} reaction, its pseudo-unimolecular reaction was derived by subtracting the \ce{CH3O2} product yields from the \mbox{\ce{CH3C(O)O2 + CH3O2}}. 
This approach was used as the \mbox{\ce{CH3C(O)O2 + CH3O2}} reaction is the most significant reaction for \ce{CH3C(O)O2}.

The rate constant for each pseudo-unimolecular reaction was taken as that of the \mbox{\ce{RO2 + CH3O2}} reaction multiplied by an `RO2' factor, which is the sum of the mixing ratios of all organic peroxy radicals. 
The \mbox{\ce{RO2 + CH3O2}} rate constant was chosen as this is the most likely reaction to occur in the atmosphere. 

\subsection{Dry Deposition}

Dry deposition velocities were taken from the MCM v3.2. 
The dry deposition velocity of MCM v3.2 species of the same chemical functional group was used for mechanism species without direct MCM v3.2 analogues. 
For example, the dry deposition velocity of PAN species in all mechanisms was equivalent to that of the PAN species in the MCM v3.2.

\subsection{Negative Product Yield Treatment}

Some mechanisms include reactions where certain products have a negative yield. 
These reactions were re-written including an operator species with a positive yield as the analysis tools used in this study does not allow use of negative product yields. 
The operator species acts as a sink for the original product by immediately reacting with the original product generating a `NULL' product. 

For example, in RADM2 the reaction of cresol (CSL) with OH has negative OH yield \reactionref{r:CSL_OH}.
\begin{reactionlist}
    \reactionitem{CSL + OH}{0.1 \ce{HO2} + 0.9 \ce{XO2} + 0.9 \ce{TCO3} - 0.9 OH}{new}{r:CSL_OH}
\end{reactionlist}
The negative OH yield was adapted to a positive operator (OHOP) yield \reactionref{r:CSL_OHOP} which then immediately reacts with OH giving a `NULL' product with a rate constant of \mbox{$8.0 \times 10^{-11}$ cm$^3$ s$^{-1}$} \reactionref{r:OHOP_OH}. 
Thus preserving the OH yields using the original mechanism.
\begin{reactionlist}
    \reactionitem{CSL + OH}{0.1 \ce{HO2} + 0.9 \ce{XO2} + 0.9 \ce{TCO3} + 0.9 OHOP}{new}{r:CSL_OHOP}
    \reactionitem{OHOP + OH}{NULL}{new}{r:OHOP_OH}
\end{reactionlist}
